Post-doc project: A complex food-web theory of stability against perturbation

### 2022-12-06 report/project_definition.Rmd
Analysis Vasseur & Fox version Brose

@@

>>>>

```{r, results = FALSE}
library(tidyverse)
library(magrittr)
library(cowplot)
library(here)

mytheme <- theme_cowplot(font_size = 10) +
background_grid() +
theme(legend.position = "bottom")

theme_set(mytheme)
```

@@

# Early results

```{r}
sim_brut <- read_csv(here("res", "hpc_test.csv"))

sim <- sim_brut %>%
  filter(!is.na(persistence), Z > .1) %>%
  mutate(sim_time_m = sim_time / 60)
```

```{r}
sim %>%
  select(rep:fr_type, persistence:sync) %>%
  pivot_longer(-c(rep:fr_type), names_to = "metric", values_to = "values") %>%
  ggplot(aes(y = log(values), x = S, color = fr_type)) +
  geom_quantile(quantiles = .5, size = 2) +
  facet_grid(rows = vars(metric), cols = vars(Z), scales = "free_y") +
  theme(legend.position = "bottom")
```

```{r}
sim %>%
  ggplot(aes(y = log(stab_com), x = S, color = fr_type)) +
  geom_jitter() +
  geom_quantile(quantiles = .5, size = 2) +
  facet_grid(cols = vars(Z), scales = "free_y")
```

```{r}
sim %>%
  ggplot(aes(y = log(sync), x = S, color = fr_type)) +
  geom_jitter() +
  geom_quantile(quantiles = .5, size = 2) +
  facet_grid(cols = vars(Z), scales = "free_y")
```

```{r}
sim %>%
  ggplot(aes(y = log(avg_cv_sp), x = S, color = fr_type)) +
  geom_jitter(alpha = .3) +
  geom_quantile(quantiles = .5, size = 2) +
  facet_grid(cols = vars(Z), scales = "free_y")
```
